Project Light

### 2015-09-09 paper/paper.tex

The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone 8.1.
In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
There are two disadvantages of this implementation, which motivated us to build a second edition:
First, experiments using the flash light for light emission showed, that there are no predictable timing behavior, e.g. the flash light was simply to slow to allow short transmission times.
This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
Secondly, in order to get reliable transmission quality, we need to become as close to real-time as possible.
This technology stack indicates bad real-time behavior, i.g. the Cordova runtime and the JavaScript interpreter could be omitted.

% bis hier hin weg

\begin{figure}
	\centering
	\includegraphics[scale=.15]{images/screen_native.png}
	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering. With a toggle switch you can choose if you want the flashlight or the screen to flicker. The length of one bit can be adjusted using a slider. Any test entered in the text filed can be transmitted by tapping on ``start''. While transmitting, the user gets feedback about the current phase right above the buttons.}
	\label{fig:screenshot}
\end{figure}

% Und den dann natuerlich noch anpassen

Hence, we built a native Android application written in Java.
Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing errors do not add up.
In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
% , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
Another advantage of this version is the flash light.
Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
Especially when attempting to program multiple motes at once this comes very handy.
To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshot}.

However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.

>>>>

The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone.
%In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
%Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
There are two disadvantages of this implementation, which motivated us to build a second edition:
The flash light cannot be controlled reliably using the mentioned web technologies.
This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
Furthermore the timing accuracy was considerably limited by the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.

% \begin{figure}
% 	\centering
% 	\includegraphics[scale=.35]{images/screenshots.png}
% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
% 	\label{fig:screenshots}
% \end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=.15]{images/screen_native.png}
	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering. With a toggle switch the user can choose if the flashlight or the screen should flicker. The length of one bit can be adjusted using a slider. Any text entered in the text field can be transmitted by tapping on ``start''. While transmitting, the user gets feedback about the current phase right above the buttons.}
	\label{fig:screenshot}
\end{figure}

To improve transmission reliability we therefore built a native Android application written in Java.
Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
% , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
%This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
Another advantage of this version is the flash light.
Depending on the smart phone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
Especially when attempting to program multiple motes at once this comes in very handy.
%To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.

%However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
% Ich glaub das diskutieren wir nicht, das passt iwie nicht zur Aussage des Papers
